---
title: "R Notebook"
output: html_notebook
---

```{r}
interval = c(0.001, 1)
```


```{r}
interval
```

```{r}
# Sample error function
em_srs <- function(C, n, s, N = Inf) {
#em_srs <- function(C, n, s, N = Inf) {
  
  # Check parameter ranges
  if (C < 0 || C > 1) {
    stop("Parameter 'C' must be in the range 0 <= C <= 1")
  }
  
  if (n <= 0 ) {
    stop("Parameter 'n' must be higher than 0")
  }

  
  if (!missing(N)) {
    if (!is.infinite(N) && (N != round(N) || N <= 0)) {
      stop("Parameter 'N' must be a positive integer or Inf")
    }
  }
  
  # Function of difference, aimed to iterate with different values of 'E'
  difference <- function(E) {
    n_theo = (qnorm(C + (1 - C) / 2, 0, 1)^2 * s^2 / E^2)
    fcf <- ifelse(is.infinite(N), 1, N / (N + n_theo - 1))
    n_adjusted <- n_theo * fcf
    return(abs(n_adjusted - n))
  }
  
  # Find the value of 'E' that minimizes the difference
  result <- optimize(f = difference, interval = c(0, 1000000))
  
  # Check if the minimum value reached the maximum value (10,000)
  #if (result$minimum == 10000) {
  #  warning("The minimum value reached the maximum value of 10,000. The result may not be reliable.")
  #}
  
  # Return the result containing the optimal (minimum) 'E' value
  return(result$minimum)
}

```

```{r}
#em_srs(C, n, s, N = Inf)
em_srs(0.95, 139, 600, 2000)
```


C=95%, p=

```{r}
np_srs <- function(C, e, p = 0.5, N = Inf) {

  # Check parameter ranges
  if (C < 0 || C > 1) {
    stop("Parameter 'C' must be in the range 0 <= C <= 1")
  }

  if (e < 0 || e > 1) {
    stop("Parameter 'e' must be in the range 0 <= e <= 1")
  }

  if (p < 0 || p > 1) {
    stop("Parameter 'p' must be in the range 0 <= p <= 1")
  }

  if (!missing(N)) {
    if (!is.infinite(N) && (N != round(N) || N <= 0)) {
      stop("Parameter 'N' must be a positive integer or Inf")
    }
  }

  # Formula to obtain the adjusted sample size
  n <- qnorm(C + (1 - C) / 2, 0, 1)^2 * p * (1 - p) / e^2
  fcf <- ifelse(is.infinite(N), 1, N / (N + n - 1))
  n_adjusted <- ceiling(n * fcf)
  return(n_adjusted)
  
  # Conclucion
  IC = c(C - e, C + e)
}
```


```{r}
p = 0.3
e = 0.05

IC = c(p - e, p + e)
IC

class(IC)

conclusion = paste("With 95% confidence, the population proportion is between",p-e,"and", p+e)
print(conclusion)
```

```{r}
N = Inf
C = 0.95
p_exp = 0.03
p_est = 0.04
e = 0.05

n_exante <- qnorm(C + (1 - C) / 2, 0, 1)^2 * p_exp * (1 - p_exp) / e^2
fcf <- ifelse(is.infinite(N), 1, N / (N + n - 1))
n_exante_adjusted <- ceiling(n_exante * fcf)

n_mustbe <- qnorm(C + (1 - C) / 2, 0, 1)^2 * p_est * (1 - p_est) / e^2
fcf <- ifelse(is.infinite(N), 1, N / (N + n - 1))
n_mustbe_adjusted <- ceiling(n_mustbe * fcf)

conclusion = paste("With 95% confidence, the population proportion is between",p_est-e,"and", p_est+e)
print(conclusion)


```


```{r}
compare_sample_sizes <- function(n_exante_adjusted, n_mustbe_adjusted) {
  if (n_exante_adjusted < n_mustbe_adjusted) {
    print("You need to increase the sample size.")
  } else {
    print("Your sample size is sufficient.")
  }
}

# Llamada a la función
compare_sample_sizes(n_exante_adjusted, n_mustbe_adjusted)

```


```{r}
sample_analysis <- function(C, e, n_real, p_est, p_exp = 0.5, N = Inf) {
  # Calculate the confidence interval
  inference <- paste0("With ",C * 100,"% confidence, the population proportion is between ", max(0, p_est - e), " and ", p_est + e)
  print(inference)
  
  # Calculate the theoretical vs needed sample size
  #n_theo <- qnorm(C + (1 - C) / 2, 0, 1)^2 * p_exp * (1 - p_exp) / e^2
  #fcf_theo <- ifelse(is.infinite(N), 1, N / (N + n_theo - 1))
  #n_theo_adj <- ceiling(n_theo * fcf_theo)

  n_needed <- qnorm(C + (1 - C) / 2, 0, 1)^2 * p_est * (1 - p_est) / e^2
  fcf_needed <- ifelse(is.infinite(N), 1, N / (N + n_needed - 1))
  n_needed_adj <- ceiling(n_needed * fcf_needed)
  
  # Analizar suficiencia de la muestra
    compare_sample_sizes <- function(n_real, n_needed_adj) {
  if (n_real < n_needed_adj) {
    print(paste("Sample variance is higher than expected. Consider increasing the sample size by", ceiling(n_real - n_needed_adj),"aditional units."))
  
#  compare_sample_sizes <- function(n_theo_adj, n_needed_adj) {
#  if (n_theo_adj < n_needed_adj) {
#    print(paste("Sample variance is higher than expected. Consider increasing the sample size by", ceiling(n_theo_adj - n_needed_adj),"aditional #units."))
    
  } else {
    print("Your sample size seems to sufficient.")
  }
}
  
  compare_sample_sizes(n_real, n_needed_adj)
}


```

```{r}
sample_analysis(C = 0.95, e = 0.05, n_real = 100, p_est = 0.35, p_exp = 0.3, N = 1000)
```


```{r}
cip_srs <- function(C, n_real, p_est, p_exp = 0.5, N = Inf) {
  
  # Check parameter ranges
  if (C < 0 || C > 1) {
    stop("Parameter 'C' must be in the range 0 <= C <= 1")
  }

#  if (e < 0 || e > 1) {
#    stop("Parameter 'e' must be in the range 0 <= e <= 1")
#  }

  if (n_real != round(n_real) || n_real <= 0) {
    stop("Parameter 'n_real' must be a positive integer")
  }
  
  if (p_est < 0 || p_est > 1) {
    stop("Parameter 'p_est' must be in the range 0 <= p_est <= 1")
  }

  if (p_exp < 0 || p_exp > 1) {
    stop("Parameter 'p_exp' must be in the range 0 <= p_exp <= 1")
  }
  
  if (!missing(N)) {
    if (!is.infinite(N) && (N != round(N) || N <= 0)) {
      stop("Parameter 'N' must be a positive integer or Inf")
    }
  }

  # Function of difference, aimed to iterate with different values of 'e'
  difference <- function(e) {
    n_theo = ((qnorm(C + (1 - C) / 2, 0, 1)^2 * p_est * (1 - p_est)) / e^2)
    fcf <- ifelse(is.infinite(N), 1, N / (N + n_theo - 1))
    n_adjusted <- n_theo * fcf
    return(abs(n_adjusted - n_real))
  }

  # Find the value of 'e' that minimizes the difference
  result <- optimize(f = difference, interval = c(0.001, 1))  
  
  e = result
    
  # Calculate the confidence interval
  inference <- paste0("With ",C * 100,"% confidence, the population proportion is between ", max(0, p_est - e), " and ", p_est + e)
  print(inference)
  
  # Compare theoretical vs needed sample size
  n_needed <- qnorm(C + (1 - C) / 2, 0, 1)^2 * p_est * (1 - p_est) / e^2
  fcf_needed <- ifelse(is.infinite(N), 1, N / (N + n_needed - 1))
  n_needed_adj <- ceiling(n_needed * fcf_needed)
  
    compare_sample_sizes <- function(n_real, n_needed_adj) {
  if (n_real < n_needed_adj) {
    print(paste("Your sample size:",n_real))
    print(paste("Needed sample size (given 'p_est'):",n_needed_adj))    
    print(paste("Consider increasing the sample size"))
    
  } else {
    print(paste("Your sample size:",n_real))
    print(paste("Needed sample size (given 'p_est'):",n_needed_adj))   
    print("Your sample size seems to sufficient.")
  }
}
  
  compare_sample_sizes(n_real, n_needed_adj)
}
```

```{r}
cip_srs(C = 0.95, n_real = 10, p_est = 0.35, p_exp = 0.3, N = 2000)
```

```{r}
cip_srs <- function(C, n_real, p_est, p_exp = 0.5, N = Inf) {
  
  # Check parameter ranges
  if (C < 0 || C > 1) {
    stop("Parameter 'C' must be in the range 0 <= C <= 1")
  }

  if (n_real != round(n_real) || n_real <= 0) {
    stop("Parameter 'n_real' must be a positive integer")
  }
  
  if (p_est < 0 || p_est > 1) {
    stop("Parameter 'p_est' must be in the range 0 <= p_est <= 1")
  }

  if (p_exp < 0 || p_exp > 1) {
    stop("Parameter 'p_exp' must be in the range 0 <= p_exp <= 1")
  }
  
  if (!missing(N)) {
    if (!is.infinite(N) && (N != round(N) || N <= 0)) {
      stop("Parameter 'N' must be a positive integer or Inf")
    }
  }

  # Function of difference, aimed to iterate with different values of 'e'
  difference <- function(e, C, p_est) {
    n_theo = ((qnorm(C + (1 - C) / 2, 0, 1)^2 * p_est * (1 - p_est)) / e^2)
    fcf <- ifelse(is.infinite(N), 1, N / (N + n_theo - 1))
    n_adjusted <- n_theo * fcf
    return(abs(n_adjusted - n_real))
  }
  
  # Find the value of 'e' that minimizes the difference
  result <- optimize(f = difference, interval = c(0.001, 1), C = C, p_est = p_est)
  
  e <- result$minimum
    
  # Calculate the confidence interval
  inference <- paste0("With ",C * 100,"% confidence, the population proportion is between ", max(0, p_est - e), " and ", p_est + e)
  
  # Compare theoretical vs needed sample size
  n_needed <- qnorm(C + (1 - C) / 2, 0, 1)^2 * p_exp * (1 - p_exp) / e^2
  fcf_needed <- ifelse(is.infinite(N), 1, N / (N + n_needed - 1))
  n_needed_adj <- ceiling(n_needed * fcf_needed)
  
  compare_sample_sizes(n_real, n_needed_adj)
}

compare_sample_sizes <- function(n_real, n_needed_adj) {
  if (n_real < n_needed_adj) {
    print(paste("Your sample size:", n_real))
    print(paste("Needed sample size (given 'p_est'):", n_needed_adj))    
    print("Consider increasing the sample size")
    
  } else {
    print(paste("Your sample size:", n_real))
    print(paste("Needed sample size (given 'p_est'):", n_needed_adj))   
    print("Your sample size seems to sufficient.")
  }
}

```


```{r}
cip_srs(C = 0.95, n_real = 30, p_est = 0.5, p_exp = 0.2, N = 2000)
```


```{r}
cip_srs <- function(C, e, p_exp = 0.5, n_real, p_est, N = Inf) {
  
  # Check parameter ranges
  if (C < 0 || C > 1) {
    stop("Parameter 'C' must be in the range 0 <= C <= 1")
  }

  if (e < 0 || e > 1) {
    stop("Parameter 'e' must be in the range 0 <= e <= 1")
  }

  if (n_real != round(n_real) || n_real <= 0) {
    stop("Parameter 'n_real' must be a positive integer")
  }

  if (p_est < 0 || p_est > 1) {
    stop("Parameter 'p_est' must be in the range 0 <= p_est <= 1")
  }

  if (p_exp < 0 || p_exp > 1) {
    stop("Parameter 'p_exp' must be in the range 0 <= p_exp <= 1")
  }

  if (!missing(N)) {
    if (!is.infinite(N) && (N != round(N) || N <= 0)) {
      stop("Parameter 'N' must be a positive integer or Inf")
    }
  }
  
  # Calculate the confidence interval
  p_upper <- round(min(1, p_est + e),2)
  p_lower <- round(max(0, p_est - e), 2)
  inference = paste0("With ", C * 100, "% confidence, the proportion in the population is between ", p_lower, " and ", p_upper)
  cat(inference, "\n")
  
  # Calculus of needed sample size, given 'e'
  n_needed <- qnorm(C + (1 - C) / 2, 0, 1)^2 * p_est * (1 - p_est) / e^2
  fcf_needed <- ifelse(is.infinite(N), 1, N / (N + n_needed - 1))
  n_needed_adj <- ceiling(n_needed * fcf_needed)
  
  compare_sample_sizes(n_real, n_needed_adj)
}

compare_sample_sizes <- function(n_real, n_needed_adj) {
  if (n_real < n_needed_adj) {
    cat("Your sample size:", n_real, "\n")
    cat("Needed sample size:", n_needed_adj, "\n")
    cat("Consider increasing the sample size\n")
  } else {
    cat("Your sample size:", n_real, "\n")
    cat("Needed sample size:", n_needed_adj, "\n")
    cat("Your sample size seems to be sufficient.\n")
  }
}

```


np_srs(C = 0.95, e = 0.05, p = 0.5, N = 10000) = 370
C, e, p_exp = 0.5, n_real, p_est, N = Inf

```{r}
cip_srs(C = 0.95, e = 0.05, p_exp = 0.4, n_real = 354, p_est = 0.5, 1000)
```
cip_srs(C = 0.95, n_real = 370, p_est = 0.5, p_exp = 0.5, N = 10000)
With 95% confidence, the proportion in the population is between 0.45 and 0.55 
Value of 'e': 0.05000287 
Your sample size: 370 
Needed sample size: 370 
Your sample size seems to be sufficient

```{r}
# Generar la población
N = 1000
set.seed(123)  # Establecer una semilla para reproducibilidad
poblacion <- runif(N, min = 5000, max = 20000)

# Calcular la media y el desvío estándar
media <- mean(poblacion)
desvio_estandar <- sd(poblacion)

# Mostrar los resultados
print(paste("N:",N))
print(paste("Media de la población:", round(media, 2)))
print(paste("Desvío estándar de la población:", round(desvio_estandar, 2)))

```

```{r}
# Sample size function
nx_srs <- function(C, E, sd_exp, N = Inf, parameter = TRUE) {

  # Check parameter ranges
  if (C < 0 || C > 1) {
    stop("Parameter 'C' must be in the range 0 <= C <= 1")
  }

  if (E <= 0) {
    stop("Parameter 'E' must be a positive number")
  }

  if (sd_exp < 0) {
    stop("Parameter 'sd_exp' must be a positive number")
  }

  if (!missing(N)) {
    if (!is.infinite(N) && (N != round(N) || N <= 0)) {
      stop("Parameter 'N' must be a positive integer or Inf")
    }
  }

  # Formula to obtain the adjusted sample size
  n = ifelse(parameter == TRUE, 
  qnorm(C + (1 - C) / 2, 0, 1)^2 * sd_exp^2 / E^2, 
  qt(C + (1 - C) / 2, N)^2 * sd_exp^2 / E^2)
  
  fcf <- ifelse(is.infinite(N), 1, N / (N + n - 1))
  n_ajusted <- ceiling(n * fcf)
  return(n_ajusted)
}


```


  n <- qnorm(C + (1 - C) / 2, 0, 1)^2 * sd_exp^2 / E^2

```{r}

nx_srs(C = 0.95, E = 50, sd_exp = 400, N = 1000, parameter = FALSE)
nx_srs(C = 0.95, E = 50, sd_exp = 400, N = 1000, parameter = TRUE)

#nx_srs(C = 0.95, E = 50, sd_exp = 400, N = 1000, parameter = FALSE)
#nx_srs(C = 0.95, E = 50, sd_exp = 400, N = 10000, parameter = FALSE)
#nx_srs(C = 0.95, E = 50, sd_exp = 400, N = Inf, parameter = FALSE)

```
```{r}

C = 0.95
E = 50
sd_exp = 400
N = 1000

#qnorm(C + (1 - C) / 2, 0, 1)^2 * sd_exp^2 / E^2, 

qt(C + (1 - C) / 2, N)^2 * sd_exp^2 / E^2
qnorm(C + (1 - C) / 2, 0, 1)^2 * sd_exp^2 / E^2


```

[1] 72
[1] 198
[1] 240
[1] 246

```{r}

C = 0.95
p_exp = 0.3
e = 0.05

n = qnorm(C + (1 - C) / 2, 0, 1)^2 * p_exp * (1 - p_exp) / e^2
Z = qnorm(C + (1 - C) / 2, 0, 1)

print(n)
print(Z)
```

```{r}
p_est = 0.4
n = 322.68
N = Inf

FC = ifelse(N == Inf, 1, ((N - n) / (N - 1)))

s_p_est = sqrt(
  (p_est * (1 - p_est) / (n - 1)) * FC
  )

LP = Z * s_p_est

print(LP)
```



```{r}
#Confidence interval function
cp_srs <- function(C,e, p_exp = 0.5, n_real, p_est, parameter = FALSE, N = Inf) {

  # Check parameter ranges
  if (C < 0 || C > 1) {
    stop("Parameter 'C' must be in the range 0 <= C <= 1")
  }

  if (e < 0 || e > 1) {
    stop("Parameter 'e' must be in the range 0 <= e <= 1")
  }

  if (n_real != round(n_real) || n_real <= 0) {
    stop("Parameter 'n_real' must be a positive integer")
  }

  if (p_est < 0 || p_est > 1) {
    stop("Parameter 'p_est' must be in the range 0 <= p_est <= 1")
  }

  if (p_exp < 0 || p_exp > 1) {
    stop("Parameter 'p_exp' must be in the range 0 <= p_exp <= 1")
  }

  if (!missing(N)) {
    if (!is.infinite(N) && (N != round(N) || N <= 0)) {
      stop("Parameter 'N' must be a positive integer or Inf")
    }
  }

  # Calculate the confidence interval

  fcf = ifelse(is.infinite(N), 1, ((N - n_real) / (N - 1)))
  
  sd_p_est = sqrt((p_est * (1 - p_est) / (n_real - 1)) * fcf)
  
  LP = ifelse(parameter == TRUE, qnorm(C + (1 - C) / 2, 0, 1), qt(C + (1 - C) / 2, N)) * sd_p_est
  
  p_upper <- round(min(1, p_est + LP), 3)
  
  p_lower <- round(max(0, p_est - LP), 3)

  inference = paste0("With ", C * 100, "% confidence, the proportion in the population is between ", p_lower, " and ", p_upper)
  
  cat(inference, "\n")

  # Calculus of needed sample size, given 'e'
  n_needed = ifelse(parameter == TRUE,
  qnorm(C + (1 - C) / 2, 0, 1)^2 * p_est * (1 - p_est) / e^2,
  qt(C + (1 - C) / 2, N)^2 * p_est * (1 - p_est) / e^2
  )

  fcf_needed <- ifelse(is.infinite(N), 1, N / (N + n_needed - 1))
  
  n_needed_adj <- ceiling(n_needed * fcf_needed)

  compare_sample_sizes(n_real, n_needed_adj)
}

compare_sample_sizes <- function(n_real, n_needed_adj) {
  if (n_real < n_needed_adj) {
    cat("Your sample size:", n_real, "\n")
    cat("Needed sample size given 'p_est' and 'e':", n_needed_adj, "\n")
    cat("Consider increasing the sample size if you want to reduce the width of the interval\n")
  } else {
    cat("Your sample size:", n_real, "\n")
    cat("Needed sample size given 'p_est' and 'e':", n_needed_adj, "\n")
    cat("Your sample size seems to be sufficient.\n")
  }
}

```

```{r}
cp_srs(C = 0.95, e = 0.05, p_exp = 0.3, n_real = 250, p_est = 0.4, parameter = TRUE, N = 5000)
```
[1] "fcf: 0.935651130226045"
[1] "sd_p_est: 0.0247146571743329"
[1] "LP: 0.048439837951947"
[1] "brecha: 0.048"
With 95% confidence, the proportion in the population is between 0.252 and 0.348 
Your sample size: 250 
Needed sample size: 304 
Consider increasing the sample size

```{r}
#Confidence interval function
cx_srs <- function(C, E, x_est, sd_exp, n_real, sd_est, parameter = FALSE, N = Inf) {

  # Check parameter ranges
  if (C < 0 || C > 1) {
    stop("Parameter 'C' must be in the range 0 <= C <= 1")
  }

  if (E < 0) {
    stop("Parameter 'E' must be a positive number")
  }

  if (n_real != round(n_real) || n_real <= 0) {
    stop("Parameter 'n_real' must be a positive integer")
  }

  if (sd_est < 0) {
    stop("Parameter 'sd_est' must be a positive number")
  }

  if (sd_exp < 0) {
    stop("Parameter 'sd_exp' must be a positive number")
  }

  if (!missing(N)) {
    if (!is.infinite(N) && (N != round(N) || N <= 0)) {
      stop("Parameter 'N' must be a positive integer or Inf")
    }
  }

  # Calculate the confidence interval
   
  fcf = ifelse(is.infinite(N), 1, ((N - n_real) / (N - 1)))
  
  sd_x_est = sd_est / sqrt(n_real) * sqrt(fcf)
  
  LP = ifelse(parameter == TRUE, qnorm(C + (1 - C) / 2, 0, 1), qt(C + (1 - C) / 2, N)) * sd_x_est
  
  p_upper <- round(x_est + LP, 3)
  
  p_lower <- round(x_est - LP, 3)
  
  inference = paste0("With ", C * 100, "% confidence, the population mean is between ", p_lower, " and ", p_upper)
  
  cat(inference, "\n")


  # Calculus of needed sample size, given 's_est'
  n_needed = ifelse(parameter == TRUE, 
                    qnorm(C + (1 - C) / 2, 0, 1)^2 * sd_exp^2 / E^2, 
                    qt(C + (1 - C) / 2, N)^2 * sd_exp^2 / E^2
                    )

  fcf_needed <- ifelse(is.infinite(N), 1, N / (N + n_needed - 1))
  
  n_needed_adj <- ceiling(n_needed * fcf_needed)

  compare_sample_sizes(n_real, n_needed_adj)
}

compare_sample_sizes <- function(n_real, n_needed_adj) {
  if (n_real < n_needed_adj) {
    cat("Your sample size:", n_real, "\n")
    cat("Needed sample size:", n_needed_adj, "\n")
    cat("Consider increasing the sample size if you want to reduce the width of the interval\n")
  } else {
    cat("Your sample size:", n_real, "\n")
    cat("Needed sample size:", n_needed_adj, "\n")
    cat("Your sample size seems to be sufficient.\n")
  }
}
```


```{r}
cx_srs(C = 0.95, E = 50, x_est = 3500, sd_est = 400, n_real = 250, sd_exp = 200, parameter = TRUE, N = 5000)
```


```{r}
#Confidence interval function
ct_srs <- function(C, E, t_est, sd_exp, n_real, sd_est, parameter = FALSE, N) {

  # Check parameter ranges
  if (C < 0 || C > 1) {
    stop("Parameter 'C' must be in the range 0 <= C <= 1")
  }

  if (E < 0) {
    stop("Parameter 'E' must be a positive number")
  }

  if (n_real != round(n_real) || n_real <= 0) {
    stop("Parameter 'n_real' must be a positive integer")
  }

  if (sd_est < 0) {
    stop("Parameter 'sd_est' must be a positive number")
  }

  if (sd_exp < 0) {
    stop("Parameter 'sd_exp' must be a positive number")
  }

  if (N != round(N) || N <= 0) {
    stop("Parameter 'N' must be a positive integer or Inf")
  }


  # Calculate the confidence interval
  
  fcf = ifelse(is.infinite(N), 1, ((N - n_real) / (N - 1)))
  
  sd_t_est = ifelse(is.infinite(N), 1, N) * sd_est / sqrt(n_real) * sqrt(fcf)
  
  LP = ifelse(parameter == TRUE, qnorm(C + (1 - C) / 2, 0, 1), qt(C + (1 - C) / 2, N)) * sd_t_est
  
  p_upper <- round(t_est + LP, 3)
  
  p_lower <- round(t_est - LP, 3)
  
  inference <- paste0("With ", C * 100, "% confidence, the population total is between ", p_lower, " and ", p_upper)
  
  cat(inference, "\n")
  

  # Calculus of needed sample size, given 's_est'
  n_needed = ifelse(parameter == TRUE, 
                    N^2 * qnorm(C + (1 - C) / 2, 0, 1)^2 * sd_est^2 / E^2,
                    N^2 * qt(C + (1 - C) / 2, N)^2 * sd_est^2 / E^2
                    )

  fcf_needed <- ifelse(is.infinite(N), 1, N / (N + n_needed - 1))
  
  n_needed_adj <- ceiling(n_needed * fcf_needed)

  compare_sample_sizes(n_real, n_needed_adj)
}

compare_sample_sizes <- function(n_real, n_needed_adj) {
  if (n_real < n_needed_adj) {
    cat("Your sample size:", n_real, "\n")
    cat("Needed sample size:", n_needed_adj, "\n")
    cat("Consider increasing the sample size if you want to reduce the width of the interval\n")
  } else {
    cat("Your sample size:", n_real, "\n")
    cat("Needed sample size:", n_needed_adj, "\n")
    cat("Your sample size seems to be sufficient.\n")
  }
}
```


```{r}
ct_srs(C = 0.95, E = 1000, t_est = 3500, sd_exp = 4.1, n_real = 200, sd_est = 6, parameter = TRUE, N = 1200)
```


